Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to get positive anxiety diagnosis for GLAD/EDGI prepan

@@

>>>>

```
###Prepan

```{r Get depression positive for GLAD/EDGI}

GLAD.prepan_mdd_positive <- GLAD.prepan %>%
  select(depressive_disorders_numeric) %>% 
  filter(depressive_disorders_numeric == 1)

GLAD.prepan_mdd_positive <- GLAD.prepan_mdd_positive %>% 
  summarise("Depressive disorders" = n())

@@

```{r Get anxiety positive for GLAD/EDGI}

GLAD.prepan_anxi_positive <- GLAD.prepan %>%
  select(anxiety_disorders_numeric) %>% 
  filter(anxiety_disorders_numeric == 1)

GLAD.prepan_anxi_positive <- GLAD.prepan_anxi_positive %>% 
  summarise("Anxiety disorders" = n())
